---
title: "Test checkr2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(checkr2)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.checker = checkr2::check_for_learnr)
```


## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

```{r two-plus-two-check}
if_matches(USER_CODE, {..(val); .(fn)(..(a), ..(b))}, 
           passif(fn == as.name("+") && a == b, "It worked!"),
           failif(fn != as.name("+"), "Use +, not {{fn}}."),
           failif(a != 2, "Sorry. The first argument must be 2."),
           failif(b != 2, "No luck. The second argument should also be 2.")
)
if_matches(USER_CODE, .(fn)(.), failif(TRUE, "{{fn}}() is a function of a single argument.") )
if_matches(USER_CODE, ..(val), failif(val != 4, "Couldn't see any matches."))
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

