---
title: "Examples for `checkr2`"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(checkr2)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.checker = checkr2::check_for_learnr)
# tutorial_options(exercise.checker = function(...) cat("Bogus checker\n"))


bunch_1_a <- function(USER_CODE) {
  code <- for_checkr(USER_CODE)
  res <- line_where(code, Z != "", 
                    message = "Remember to store the result under the name `Id`.")
  res <- line_where(res, Z == "Id", message = "Use `Id` for the assignment, not {{Z}}.")
  
  res <- line_where(res, F == rep, message = "You're supposed to use `rep()`.")
  the_each_arg <- named_arg(res, "each", 
                         message = "Look at the help for `rep()` to see what arguments are available to control the pattern of repetition. (These are documented under `...`)")
  t1 <- check(the_each_arg,
              failif(V != 3, 
                     "Good use of `each=`, but each = {{V}} is not the right value."))
  if (failed(t1)) return(t1)
  
  the_vector <- vector_arg(res, message = "Where do you create the elements to be repeated?")
  t2 <- check(the_vector, 
              failif(! identical(V, 1:4), 
              "The elements to be repeated are 1 through 4, not {{V}}. Where do you construct the set 1:4 to pass to `rep()`?"))
  
  

  t2 
}
```


```{r eval = FALSE}
# For testing ...
ex1 <- quote(c(1,1,1,2,2,2,3,3,3,4,4,4))
ex1a <- quote(Id <- c(1,1,1,2,2,2,3,3,3,4,4,4))
ex2 <- "Id <- rep(1:3, each = 3)"
ex2a <- "Id <- rep(1:3, each = 4)"
ex2b <- "Id <- rep(3, each = 4)"
ex3 <- "Id <- rep(1:4, each = 3)"

# bunch_1_a(ex1)
# bunch_1_a(ex1a)
# bunch_1_a(ex2)
# bunch_1_a(ex2a)
# bunch_1_a(ex3)

```
```


## Using `rep()`

a. Create a vector named `Id` that has contents `1 1 1 2 2 2 3 3 3 4 4 4`. Use the `rep()` function to do this.
```{r bunch-1-a, exercise = TRUE, echo = FALSE}

```

```{r bunch-1-a-solution, echo = FALSE}
Id <- rep(1:4, each = 3)
```

```{r bunch-1-a-hint-1, echo = FALSE}
1:4
```

```{r bunch-1-a-hint-2, echo = FALSE}
rep(1:4, .... = 3) 
```

```{r bunch-1-a-code-check, echo = FALSE}
1 # There must be something in this chunk.
```

```{r bunch-1-a-check, echo = FALSE}
bunch_1_a(USER_CODE)
```






b. Create a vector named `Letter` that contains `"a" "b" "c" "a" "b" "c" "a" "b" "c" "a" "b" "c"`
```{r bunch-1-b, exercise = TRUE, echo = FALSE}

```

```{r bunch-1-b-solution, echo = FALSE}
Letter <- rep(c("a","b","c"), each = 4)
```

```{r bunch-1-b-hint-1, echo = FALSE}
c("a", "b", "c")
```

```{r bunch-1-b-hint-2, echo = FALSE}
rep(...., length.out = 12)
```

```{r bunch-1-b-code-check, echo = FALSE}
1 # chunk can't be empty
```

```{r bunch-1-b-check, echo = FALSE}
# For testing ...
#USER_CODE <- "Letter <- rep(c("a","b","c"), each = 4)"
bind(USER_CODE, ".(fn)(...)",
           failif(fn != quote(`<-`), "Remember to store the result under the name `Letter`."))
bind(USER_CODE, {..(res); `<-`(.(nm), .(val))},
           failif(nm != quote(Letter), "The object should be called `Letter`, not '{{nm}}'."),
           bind(val, rep(..(a), `..(nm)` = ..(arg2)),
                      failif(nm != "each", "Look at the help for `rep()` to see what arguments are available to control the pattern of repetition. (These are documented under `...`)"),
                      failif( ! identical(a, c("a", "b", "c")),  "The elements to be repeated are `\"a\", \"b\", \"c\"`, not {{a}}. Where do you construct that set to hand to `rep()`?")),
           passif(identical(res, rep(c("a","b","c"), each = 4)), "Right!"),
           failif(TRUE, "Sorry, but the result isn't right."))

```


c. You've constructed `Id` in the previous exercise. Copy the statement you used to do that into this code block. Then create two more vectors:
    1. `x` which will be evenly spaced numbers between 1 and 43. `x` will have the same length as `Id`.
    2. `y` which will be similar to `x`, but will consist of evenly spaced numbers between -20 and 0.
    
Once you have constructed `x` and `y`, make a data frame called `df` that contains `x`, `y`, `Id` as columns. The variable names should be `x`, `y`, and `Id`.

```{r bunch-1-c, exercise = TRUE, echo = FALSE}

```

```{r bunch-1-c-solution, echo = FALSE}
Id <- rep(1:4, each = 3)
x <- seq(1, 43, along.with=Id)
y <- seq(-20,0, along.with=Id)
df <- data.frame(x = x, y = y, Id = Id)
```

```{r bunch-1-c-check, echo = FALSE}
# USER_CODE <- quote({Id <- rep(1:4, each = 3);
#   x <- seq(1,42, along.with = Id);
#   y <- seq(-20, 0, along.with = Id);
#   df <- data.frame(x = x, y = y, Id = Id)
# })

fail_if_no_match(USER_CODE, Id <- ., "You didn't create `Id` as requested.")
bind(USER_CODE, `<-`(Id, ..(val)),
           failif( ! identical(val, rep(1:4, each = 3)), 
                   "You didn't make `Id` correctly. "))
fail_if_no_match(USER_CODE, x <- ., "You didn't create `x` as requested.")
bind(USER_CODE, `<-`(x, ..(val)),
           failif( ! identical(val, seq(1, 43, length = 12)),
                   "You didn't make `x` correctly."))
fail_if_no_match(USER_CODE, y <- ., "You didn't create `y` as requested.")
bind(USER_CODE, `<-`(y, ..(val)),
           failif( ! identical(val, seq(-20, 0, length = 12)),
                   "You didn't make `y` correctly."))
fail_if_no_match(USER_CODE, df <- ., "You didn't create `df` as requested.")
bind(USER_CODE, `<-`(df, ..(df)),
           failif( ncol(df) != 3, "The data frame `df` should have three columns, not {{ncol(df)}}."),
           failif( ! setequal(names(df), c("Id", "x", "y")), "The names of the data frame variables should be `Id`, `x`, `y`. You've got {{paste(paste0('`', names(df), '`'), collapse=', ')}}."))
bind(USER_CODE, `<-`(df, .(fn)(...)),
           failif(fn != quote(data.frame), "Use the `data.frame()` function to make the data frame"))
           
pass_anyways()


```

